---
title: "Linear Model"
author: "Sabrina A"
date: "7/14/2021"
output: html_document
---

```{r setup, include=FALSE}
require(tidyverse)
require(tigerstats)
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 
```

###Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```

SIMS is on the y-axis and ARM is on the x-axis. This plot shows a positive linear correlation. The SIMS increase as does the size of the ARM.

# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The value is 0.68, which is a positive number. This indicates the line will travel upwards towards the right of the graph.

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation that for the line that fits the graph is SIMS = -4.1 + .05 * ARM. The formula used y=mx+b to create the line. The Adjusted R-square is the number to look at when translating the metric.
(y=SIMS),(m=-4.1),(x=ARM),(b=.05)

# now add the model fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

It seems the value of (y-intercept)SIMS is just a little over 1.
